Convex optimisation in communications with \texttt{cvxpy}

### 2017-10-13 article_cvxpy.tex
added email addresses, moved plots a bit

\title{Convex optimisation in communications with \texttt{cvxpy}}
\author{Robert P.~Gowers}%
\author{Sami C.~Al-Izzi}%
\author{Timothy M.~Pollington}%
\author{Roger J.~W.~Hill}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Keith Briggs}
\affiliation{BT, Adastral Park}
\maketitle

@@

Here we show that an interesting problem in communications has a convex formulation that can be easily implemented computationally using the \texttt{cvxpy} \textit{Python} module. This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering. First let us introduce some basic convexity concepts.

@@

\noindent A function $f$, where $f:\mathbb{R}^n \rightarrow \mathbb{R}$, is \textit{convex} if $\forall x,y\in \textbf{dom} f$ and $0 \leq \theta \leq 1$ \cite[p.67]{cvxpybook}:
\begin{align}
f(\theta x + (1-\theta)y) \leq \theta f(x)+(1-\theta)f(y).
\end{align}
This means that the function is less than or equal to linear, as shown in Fig.~\ref{fig:convex}. %A concave function can be made convex by the operation $f\to-f$.
\begin{figure}[h!]
\includegraphics[width=0.9\linewidth]{convex_function.pdf}
\caption{\label{fig:convex}A chord showing convexity of the function $x^4$.} 
\end{figure}

@@

@@

>>>>

\title{Convex optimisation in communications with \texttt{cvxpy}}
\author{Robert P.~Gowers}%
\email{r.gowers@warwick.ac.uk}
\author{Sami C.~Al-Izzi}%
\email{s.al-izzi@warwick.ac.uk}
\author{Timothy M.~Pollington}%
\email{t.pollington@warwick.ac.uk}
\author{Roger J.~W.~Hill}%
\email{r.hill.3@warwick.ac.uk}
\affiliation{Department of Mathematics, University of Warwick}
\author{Keith Briggs}
\email{keith.briggs@bt.com}
\affiliation{BT, Adastral Park}
%\affiliation{r.gowers@warwick.ac.uk}
\maketitle

@@

Here we show that an interesting problem in communications has a convex formulation that can be easily implemented computationally using the \texttt{cvxpy} \textit{Python} module. This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering. First let us introduce what convexity means.

@@

\noindent A function $f$, where $f:\mathbb{R}^n \rightarrow \mathbb{R}$, is \textit{convex} if $\forall x,y\in \textbf{dom} f$ and $0 \leq \theta \leq 1$ \cite[p.67]{cvxpybook}:
\begin{align}
f(\theta x + (1-\theta)y) \leq \theta f(x)+(1-\theta)f(y).
\end{align}
This means that the function is less than or equal to linear, as shown in Fig.~\ref{fig:convex}. %A concave function can be made convex by the operation $f\to-f$.

@@

\begin{figure}[h!]
\includegraphics[width=0.9\linewidth]{convex_function.pdf}
\caption{\label{fig:convex}A chord showing convexity of the function $x^4$.} 
\end{figure}

@@

\subsection*{Author Biography}
Robert Gowers, Sami Al-Izzi, Timothy Pollington and Roger Hill are PhD students in the Mathematics for Real-World Systems CDT at the University of Warwick.  Keith Briggs is a senior research mathematician at BT.
